DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-01-27 rebuttal.tex

% MATH SYMBOLS
\newcommand{\1}{\b{1}}              % all-ones vector
\newcommand{\0}{\b{0}}              % all-zero vector
\newcommand{\g}[1]{\b{#1}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\B}{\mathcal{B}}
\renewcommand{\L}{\b{L}}
\newcommand{\tL}{\tilde{\L}}
\newcommand{\W}{\b{W}}
\newcommand{\I}{\b{I}}
\newcommand{\D}{\b{D}}
\newcommand{\U}{\b{U}}
\newcommand{\x}{\b{x}}
\newcommand{\X}{\b{X}}
\newcommand{\y}{\b{y}}
\newcommand{\Y}{\b{Y}}
\newcommand{\bu}{\b{u}}
\newcommand{\f}{\b{f}}
\newcommand{\trans}{^\intercal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\bLambda}{\b{\Lambda}}
\newcommand{\blambda}{\b{\lambda}}
\newcommand{\bO}{\mathcal{O}}
\newcommand{\T}{\mathcal{T}}
\DeclareMathOperator*{\esp}{E}
\DeclareMathOperator*{\var}{Var}
\DeclareMathOperator*{\vect}{vec}
\DeclareMathOperator*{\argmin}{arg \, min}
\newcommand{\pkg}[1]{\texttt{#1}}

\begin{document}
\maketitle

% Note: it is very convenient to refer to other comments using the referencing system of \LaTeX, such as here see  \autoref{comment:errorEq2}.

The authors would like to thank the reviewers for their comments, which significantly helped improve the manuscript. We believe we have addressed all the issues raised in the following rebuttal. 
%  For each comment, we have first highlighted the issue, then we provided an answer, and finally we described how the manuscript was adjusted.

@@

\subsection{}
\begin{mdframed}[style=comment] 
One fairly significant concern I have is how convincing the application to other machine learning algorithms is. The authors compare deep sphere to a SVM classifier, in the case of distinguising from two cosmological models from density maps. This classification is obviously a simplification of what would be done in real comsological analyses, but is sufficient for the purpose of demonstration here. However, the metrics adopted do not clearly highlight the superiority of DeepSphere. The SVM takes pixel histograms or power spectrum densities (PSDs) of each input map. It is not surprising that DeepSphere outperforms them given that it takes the whole map as input. Histograms and PSDs are very restrictive compressions of the data - dropping a lot of spatial information. An SVM or even a standard fully connected neural network (NN) would perform a lot better. It is unclear how that would compare to DeepSphere. But I would certainly expect DeepSphere to be a lot easier to train and have many fewer parameters, which I think is the key advantage that needs to be highlighted here. This is analogous to comparing a standard convolutional NN to a standard fully-connected NN. With appropriate depth both will extract the same information and perform equally well. But of course the CNN has fewer parameters and is easier to train since its structure naturally extracts spatial information. One wouldn't compare the CNN to a SVM trained on pixel histograms or PSDs, since those would not have access to the same information. It would be more natural to compare the CNN and the NN trained on the same maps, and examine the number of parameters, the time and number of examples needed for training to achieve the same performance, etc. This would truly highlight how the structure of the NN is a key advantage.
\end{mdframed}

\todo{Assigned: @nati, @michael}
The intuition of the reviewer is correct. Theoretically, using the raw data, \emph{an SVM or even a standard fully connected neural network (NN) would perform a lot better.} In practice, this those models are limited by the computational power and the dataset size.

We actually tried training an SVM on the raw data but were unable to obtain over $60\%$ accuracy in the easiest cases where all the other tested models were close to $100\%$. Practically, the classifier would either overfit or be over-regularized. For that reason, we decided, not to report the raw-data SVM results in the paper.  
\nati{FYI, I did try again to be entirely sure about it.}

A model based on a fully connected neural network, as suggested by the reviewer, contains a very large number of weights which severely restricts what can be tested with conventional hardware. In our case the input number of pixels (for order $1$) is $1024^2$ which limits the number of neurons that can be used in the architecture. For the completeness of this answer, we did try a fully connected NN. Practically, in the first layer, we were only able to $128$ neurons before hitting an out of memory errors. In this setting, with a relative amount of noise of $0.5$, we were unable to regularize the network such that it would actually classify the validation set. Note that all reported classifiers performed well (close to $100\%$ accuracy) in this particular setting. Similar conclusions were observed with other settings.
%Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical
structure of the HEALPix sampling. , even when increasing the number of neurons for small part of the sphere (order $2$ and $4$).

This being said, the reviewer comment is justified and we will add this information to the paper.

\todo{Add it in the paper... Make clear that CNN is so much better than fully connected + say that SVM on the raw features does not work.}

@@

We clarified the sentence with this:
\begin{mdframed}[style=manuscript] 
blabla
\end{mdframed}
}

\subsection{}
\begin{mdframed}[style=comment] 
"Our graph is constructed as an approximation of sphere S2, a 2D manifold embedded in R3, Indeed, [33] showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity. While our construction will not exactly respect the setting defined by [33], we observe empirically strong evidence of convergence." This paragraph is unclear. Could you please add a few words to clarify what the approach of 33 is? 
\end{mdframed}

\todo{Assigned: @nati, @michael}

We tried to clarify the paragraph in the following manner:
\begin{mdframed}[style=manuscript] 
Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
Indeed, \cite{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
While our construction will not exactly respect the setting defined by \cite{belkin2007convergence} (the sampling is not uniform and the graph is not fully connected), we observe empirically strong evidence of convergence.
\end{mdframed}
We are aware that this particular point could be more detailed. Nevertheless, we believe that a deeper discussion does not belong to this paper. In fact, we are currently investigating the convergence question with the goal of obtaining better graph constructions or rotational equivariance results.

@@

\subsection{}

\begin{mdframed}[style=comment] 
Figure 3: What was resolution used for those maps? Does the projection of the eigenvectors depend on the resolution and band-limit? 
\end{mdframed}

\todo{Assigned: @nati}
We were actually limited in resolution when computing the graph Fourier eigenvectors as diagonalizing the Laplacian matrix scales as $O(N_{pix}^3)$. Hence we used a resolution of $N_{side}=16$. The information has been added to the paper.

Since we do not have any convergence result yet, we are not sure about how the projection error evolves. However, if there is convergence (and we believe there is), then the eigenvectors associated with the lowest $\ell$ probably converge first.

@@

\subsection{}
\begin{mdframed}[style=comment] 
Page 7: "That is much more efficient than filtering with spherical harmonics, even though HEALPix was de- signed as an iso-latitude sampling that has a fast spherical transform. That is especially true for smooth kernels which require a low polynomial degree K. Figure 4 compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here. A naive implementation of our method is ten to twenty times faster for Nside = 2048, with K = 20 and K = 5, respectively, than using the spherical harmonic transform at lmax = 3Nside implemented by the highly optimized libsharp [38] library used by HEALPix." This is not so clear. Is the graph method also performing a Gaussian smoothing with the same characteristics? If so, what are those? How precise is the graph convolution approximating the true harmonic-space Gaussian convolution in this case? This is relevant since some approximations (for instance when analyzing cosmic microwave background data) require high-precision Gaussian smoothing. Finally, is lipsharp optimizing Gaussian smoothing in any way?
\end{mdframed}
\todo{Assigned: @nati,
Tocheck: @tomek, @michael
}

In the experiment shown if Figure 4, we only care about speed and not about the filter itself (we could have chosen any filter). The main reason is that in the context of neural networks, filters will be learned and hence is not predefined. 
While, libsharp is probably not optimized for Gaussian smoothing, in this experiment we intend to report on the general filter speed and use conveniently a Gaussian.

We note that, the reviewer question is interesting. Replacing spherical filtering (using the harmonic decomposition) with graph filtering might be possible in the future as suggested by Appendix C and fig 14.
Our feeling is that in its current state, it probably does not have the required precision to be usable in a high precision setting. Nevertheless, theoretical improvement on the convergence side could potentially make it competitive.

@@

I will happily recommend this paper for publication. Firstly though, I would like access to the data (privately rather than via emailing the group) so that I can check the notebooks thoroughly. The notebooks are extremely well written but I would like to run them first. As well as this I think there are a few extra applications which will improve the manuscript further, and make the method more appealing for users. I would recommend that these ideas are at least seriously considered by the authors and hopefully implemented: 
\end{mdframed}

\todo{Assigned @Tomek
\begin{itemize}
  \item Thank the reviewer
  \item give him access to data
\end{itemize}}

\subsection{}

\begin{mdframed}[style=comment] 
The first, and most important is an example using masks. Since the authors mention how their method should in principle work well with masks, especially in comparison to HEALPix and Clebsh-Gordan transform spherical harmonic methods I think that it would be extremely enlightening to present this work, probably in the form of a performance vs. time plot. With this being done, the informational content of a masked version of the cosmological application could easily be included. This would, I'm sure, be attractive to the cosmological community as well as the ML community who are always looking for good ways to deal with masked data.
\end{mdframed}
\todo{Assigned: @Michael, @Nati}
Our implementation is actually already working with a mask, we choose to use parts of $1/12$, $1/48$ and $1/192$ of the total sphere. Our main motivation was to build a "large" dataset with a relatively low number of cosmological maps. 
In terms of neural network, the available implementation of \cite{cohen2018sphericalcnn,kondor2018clebsch} for spherical CNNs and Clebsh-Gordan CNNs are not scalable enough to be trained on the cosmological maps dataset and do not use the HEALPix sampling. Hence a comparison with these methods requires a different setting, which far beyond the scope of our contribution. Nevertheless, this comparison is important and we are preparing a second contribution where it will be conducted.

@@

\begin{mdframed}[style=comment] 
Secondly, using only SVM as a comparison might skew how well this technique appears to works in a deep learning setting. In principle (and I say this not knowing for sure) 2D CNNs should probably be able to work as well as DeepSphere (although no where near as elegantly) by taking in a projected 2D image of the sky and using *loads* of filters to learn about the distortion at different parts of the projected sky. It would be interesting (and I think a fairly easy test) to check how well DeepSphere performs against a 2D CNN on projections. 
\end{mdframed}
\todo{Assigned: @Nati, @Michael, @Tomek}

\nati{\textbf{Very important point!!!}
\begin{itemize}
  \item We can do this comparison...
  \item Since we used 1/12 of the sphere, all the pixel grids we use are somehow squared. I am now using this as a projection. @Tomek, do you know if this is ok? Or do you know how to do the projection in a simple and efficient manner? 
  \item I think that traditional 2D CNNs will be as good as our algorithm. We should be very careful in the way we formulate this in our answer and in the paper.
\end{itemize}
}

\begin{mdframed}[style=comment] 
Similarly, I think it would useful to check how well the DeepSphere CNN does against the FCN when the input data is rotated randomly during training - I imagine that the results should match or probably exceed the FCN results and I think this would be a neat little test which doesn't involve needing extra data, just more augmentation.
\end{mdframed}
\todo{Assigned: @Nati, @Michael, @Tomek}

Theoretically, providing that the FCN and the CNN have the same modelisation power (i.e, the FCN does not have more or larger layers) and assuming the convolution would be truly invariant to rotation, the CNN could never exceed the FCN for truly rotational invariant data. However, assuming enough augmentation (as suggested by the reviewer) and training, the CNN should get to the level of the FCN. In practice, this would require more training as the CNN has to learn the invariance. 
The point of defining a FCN instead of a CNN is to avoid the complexity of augmenting the dataset. Hence we did not implement it. Nevertheless, it is an interesting point worth discussion in the paper. We updated the manuscript accordingly.
\todo{Do it}

@@

\begin{mdframed}[style=comment] 
I should say, even though I made the above comments, I thought the paper was really excellent and well written. There were a couple of very minor points which I would like the authors to expand slightly on or consider.
\end{mdframed}
Thank you very much for your comments. We addressed them to the best we could.

\subsection{}
\begin{mdframed}[style=comment] 
While our construction will not exactly respect the setting defined by [33], we observe empirically strong evidence of convergence.

- Could you add a plot comparing the graph Laplacian as a function of number of pixels and the Laplace-Beltrami operator so the reader can explicitly see the convergence?
\end{mdframed}

This is a good question and a fair request. Problematically, we cannot provide such a plot without solving the theoretical problem first. Indeed to experimentally show convergence, we actually need to build a series of graph Laplacian that converges toward the Laplace Beltrami operator. This far more complicated than building one Laplacian and observe some similarities between the two operators.

@@

\subsection{}

\begin{mdframed}[style=comment] 
We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.

- Are you really going to search through different weighting schemes in future work? I would be interested if you were, but could you speculate on what you expect to achieve by looking at different ones?
\end{mdframed}

Yes, we are investigating the question of graph weights.
As suggested in the previous comment, the weighting scheme used is very important for the graph Laplacian to approach the true Laplace Beltrami operator. Using a more appropriate weighting scheme, one could hope for a more rotational invariant convolution and a faster convergence rate of the operator. 
\nati{@michael, how much shall we say here?}

@@

\subsection{}
\begin{mdframed}[style=comment] 
Thanks to the softmax, the output $\bf{y}\in\mathbb{R}^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.

- This is a common misconception which is incorrect and needs restating. It is *not* a probability distribution for the class, rather it is a discretised conditional distribution for the class given both the data and the weights and biases of the trained network. One way to see that the value of $y_i$ cannot be considered a probability (which implies P(y|x), i.e. the probability of a class given the data) is that if the network is untrained, would you retrieve back the correct probability? It's wholly dependent on the network.
\end{mdframed}

We agree with the reviewer. We actually misformulate this sentence. We have reformulated it as:
\begin{mdframed}[style=manuscript] 
Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the confidence of the network that the input sample belongs to class $i$. Note that in general, this probability distribution does not correspond to the true posterior distribution $p(y|x)$.
\end{mdframed}

@@

\subsection{}
\begin{mdframed}[style=comment] 
Than can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.

- I think you mean "This" rather than "Than". I think, however, you are making a more important point here than you realise. It is not really "intrinsic data augmentation" but rather building a NN to suit your purposes. This should be done by the entire community as, at the moment, too many people blindly build their networks without considering their data and then struggle to get the best results out. The symmetries of the data should be the first thing to influence architecture of a network, exactly as you have reasoned. You might want to add a statement about how you know what your symmetries are and thus, you know how to build a well reasoned network which is more likely to work (and that other should do the same).
\end{mdframed}
\todo{Assigned: @michael}

\subsection{}
\begin{mdframed}[style=comment] 
As such, the SHT is only performed once on the input (no back and forth SHT between each layer). While this clever trick lowers the complexity of the convolution to $\mathcal{O}(N_{pix})$, the non-linearity is $\mathcal{O}(N^{3/2}_{pix})$.

- I don't understand what the difference is between the convolution and the "non-linearity". I think this sentence either needs explaining further. Is the process $\mathcal{O}(N_{pix})$ or $\mathcal{O}(N^{3/2}_{pix})$?
\end{mdframed}
In the work of \cite{kondor2018clebsch}, the convolution is performed in the spectral (harmonic) domain with a simple Adamar product. Instead of recomposing the signal and applying a traditional non-linearity such as "relu" in the pixel domain, \cite{kondor2018clebsch} proposes to directly apply a Clebsch–Gordan product in the spectral domain. As a non-linear operation preserving the rotation equivariance, it is considered as the non-linearity of the neural network.

We have modified the manuscript as:
\begin{mdframed}[style=manuscript] 
While this clever trick lowers the complexity of the convolution (Adamar product in the spectral domain) to $\bO(N_{pix})$, the non-linearity (Clebsch–Gordan product) is $\bO(N_{pix}^{3/2})$.
\end{mdframed}
\nati{Should we be clearer in the paper?}

\subsection{}
\begin{mdframed}[style=comment] 
When mentioning that you are 10 to 20 times faster than the SHT it should be noted that libsharp has amazing distributed mpi functionality which helps, although of course your method is genuinely lower order computationally (and can be distributed simply on a GPU).
\end{mdframed}
When comparing the speed, we used a single-core CPU implementation of the graph convolution. We believe that this comparison is fair.
\nati{Is this sufficient?}

\subsection{}
\begin{mdframed}[style=comment] 
In Appendix A. (my personal favourite part) could you measure the percent difference that different eigenvectors differ from the spherical harmonics due to incomplete discretisation of the sphere, perhaps plotting side by side plots like Figure 3, but with SH too (or their differences). By the way, Figure A.12 is placed in the wrong section.
\end{mdframed}
\todo{Assigned: @nati, @michael}
We added a figure showing the percentage of mis-alignment with the spherical harmonics. We also moved Figure A.12 in the correct subsection.

\begin{center}
\includegraphics[width=0.5\linewidth]{figures/subspace_alignment_percentage.pdf}
\end{center}

@@

\subsection{}
\begin{mdframed}[style=comment] 
In Appendix C. is there a connection between $t$ and $\sigma$ that you can make, or do you just fit them to be similar? If you just fit them to be similar I'm not sure where the relative differences come from. If they are related, however, then the relative differences make sense, but I can't see what the connection is.
\end{mdframed}

In the current version of the manuscript and the code, we simply fitted a few $t$ to match the different $\sigma$. In theory, there should be a connection between the two values providing the graph Laplacian has converged toward the Laplace Beltrami operator. Again, this is left for a futur contribution.

### 2019-01-27 rebuttal.tex

\subsection{}
\begin{mdframed}[style=comment] 
A question that I would like to know personally, are you thinking about a future upgrade to non-radial kernels?
\end{mdframed}
We are thinking about it. However, as the graph framework we are using only works with radial filters, it is not a simple question. One simple trick to make the network sensitive to direction is to add a per-channel fully connected layers. We are currently investigating other potential graph techniques that would lead to non-radial kernels.

\subsection{Details}
\begin{mdframed}[style=comment] 
Finally, I noticed a few points in the text where there were typos or things which were difficult to follow and I have put a note of them below and tried to correct them as much as I can so that you don't have to put too much effort in - I can't wait to see this paper published. Sorry that the list is so extensive (I'm a bit of a stickler for details and trying to write papers concisely):
\end{mdframed}
\todo{Assigned @tomek. 
This reviewer really spend the time. Should we say something here?}

@@

\begin{mdframed}[style=comment] 
Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision of the parameter estimation [9–16].

- There are many of us in the community who are not overly keen on "precision" of parameter estimation being the target for machine learning. Rather, we would prefer robustness of parameter estimation. It might be worth changing this sentence a bit so as not to upset some of the referenced authors ;)
\end{mdframed}
\todo{Assigned: @tomek, @michael}

\begin{mdframed}[style=comment] 
When you have multiple = in equations could you split them on to separate lines? This would make the logical steps for following the equations a lot clearer.
\end{mdframed}
\todo{Assigned: @tomek}
\nati{I personally think it is better without separating the lines}

@@

\begin{mdframed}[style=comment] 
You change a lot between "node", "vertex" and "pixel". Could you stick to one of these? I think that "vertex" or "pixel" makes the most sense ("pixel" due to the HEALPix pixelisation of the maps or vertex because of the use of the $v$ notation). Node is quite confusing in several places because there is an inherent connection between node and neuron in ML literature, and since there is swapping between the three different terms it's a little hard to keep track.
\end{mdframed}
\todo{Assigned: @all}
\nati{What do you think? This avoid repetition. But we could be more consistent...}

\begin{mdframed}[style=comment] 
You change between math font and text font for the names of your layers when inside and outside of equations. It would look a lot neater sticking with one choice. (Sorry, that seems quite petty and I don't mean it to be).
\end{mdframed}
Thank you for the suggestion. We have made the paper consistent.
\nati{@all, when you read the paper, please check that I did not forget some of them. Every layer has been changed to math symbols as we use them like function. For example, SM becomes $SM$.}

@@

\begin{mdframed}[style=comment] 
In Appendix C. you talk about Kroneker a lot, but earlier you talk about Kroneker $\delta$ (which is it's correct name). It's probably worth sticking with the full name.
\end{mdframed}
We have modified the manuscript according to the reviewer suggestion.

\begin{mdframed}[style=comment] 
Sky maps are rotation invariant: rotating maps on the sphere doesn’t change their interpretation, as only the statistics of the maps are relevant.
- I think that you mean that rotating maps on the sphere doesn't change their interpretation *when* only the statistics of the maps are relevant. Say you wanted to compare the NGC against the SGC, then rotating the map would obviously change the results.
\end{mdframed}
This sentence has been reformulated as:
\begin{mdframed}[style=manuscript] 
We consider the sky maps rotational invariant as in our case rotating maps on the sphere doesn't change their interpretation since only the statistics of the maps are relevant.
\end{mdframed}

@@

\begin{mdframed}[style=comment] 
Given a map $\bf{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\bf{y}\in\mathbb{R}^{N'_{pix}}$ such as

- It should be "such that" not "such as". "Given a map $\bf{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\bf{y}\in\mathbb{R}^{N'_{pix}}$ such that"
\end{mdframed}
Thank you for spotting this mistake. We have corrected the manuscript.

\begin{mdframed}[style=comment] 
... where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix}/N'_{pix}$ is the down-sampling factor, which for HEALPix is $|\mathcal{C}(i)| = N_{pix}/N'_{pix} = (N_{side} / N'_{side})^2 = 4^p$.

- Can you explain what $p$ is and it would probably be worth splitting this equation into a multi-line align environment for clarity.
\end{mdframed}
In fact, $p$ is defined as $p=\log_2(N_{side} / N'_{side})$. We have updated the manuscript with this clarification and with an equation environment.

@@

\begin{mdframed}[style=comment] 
We emphasize that the cost function and the SM layer is the sole difference between a neural network engineered for classification or regression.

- This should be "We emphasise that the cost function and the SM layer are the sole differences between a neural network engineered for classification or regression."
\end{mdframed}
We thank the reviewer for spotting this mistake. We have updated the manuscript.

\begin{mdframed}[style=comment] 
The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = E\left[C\left(NN_\theta(\bf{X}),\bar{\bf{Y}}\right)\right]$.

- It is the goal of training, not of learning (in common parlance anyway). Also, you should say that E[] is the expectation rather than leaving people to guess according to the next sentence.
\end{mdframed}
\todo{Assign:  @nati, @michael. \nati{@micheal, please check this one carefully, also in the text, I am not sure my notation is correct}}

According to us, the goal of training is to minimize the empirical risk, which does not contain the expectation. On the contrary, the goal of learning is to minimize the expected risk, i.e. we additionally do not want to overfit the training set. Hence we left "learning" in the text. Nevertheless, we specified the expectation operator.

@@

- It should be "which makes it computationally efficient" instead of "what". (It's possibly "that" and not "which", but I'm never sure which ;))
\end{mdframed}
This mistake has been corrected.

\begin{mdframed}[style=comment] 
A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg’s uncertainty principle.

- What do you mean by "by Heisenberg’s uncertainty principle." That seemed to come out of nowhere. This needs explaining further.
\end{mdframed}
\todo{Assigned: @all}

\nati{The reviewer is correct. Our justification is shaddy. I am not sure how to make this clear, without writing too much. It is kind of a general consent that smoothness in one domain implies localization in the other. The reason is that for the continuous Fourier transform, we have:
\begin{equation*}
\widehat{f(t\cdot)}(\omega)=\frac{1}{t}\hat{f}\left(\frac{\omega}{t}\right). 
\end{equation*}
Hence by concentrating $f$ in the time domain, i.e. making $t$ smaller, we also reduce the derivative of $\widehat{f(t\cdot)}$ in the spectral domain, making it smoother.
Heisenberg uncertainty principle bounds the concentration in both domains simultaneously, i.e. we have (to be checked if added to the paper)
\begin{equation*}
\text{var}({f})\text{var}({\hat{f}}) \geq \frac{1}{16 \pi^2}
\end{equation*}
Hence the theorem says that you cannot concentrate arbitrarily in one domain without de-concentrating in the other.

@@

\begin{mdframed}[style=comment] 
This standard deviation has the property to keep the energy of the signal more or less constant across layers

- Should be "of keeping" instead of "to keep". "This standard deviation has the property of keeping the energy of the signal more or less constant across layers"
\end{mdframed}
We corrected the manuscript.

\begin{mdframed}[style=comment] 
We derived this rule from the Chebyshev polynomial equations and some empirical experiments.

- This is a bit loose, can you explain further and add a citation if you didn't do the experiments yourself?
\end{mdframed}
\todo{Assign: @nati, @michael}
\nati{We would need an appendix to do that. It is the last figure of the figure’s notebook (expected filter). I could spend two hours and write some equation... @michael, what do you think?}

@@

\begin{mdframed}[style=comment] 
Figure 10: Random selection of 24 learned filters from the fifth spherical convolutional layer L5. Top: section. Bottom: gnomonic projection.

- There is not enough information in this caption. Can you explain that there is some obvious peak structure. I think a colourbar on the gnomonic projection would be useful too.
\end{mdframed}
\todo{Assign: @all}
\nati{The problem is that random filters are picky as well and look very similar. Should we say that? I do not think a colorbar is necessary since there are numbered axes on the top plots. Do you agree?}

We decided not to add a colorbar as scale information is already present in the top plot of the figure.

@@

\begin{mdframed}[style=comment] 
In this case, the graph setting used through this contribution correspond to assume reflective border conditions.

- It should be "assumed". "In this case, the graph setting used through this contribution correspond to assumed reflective border conditions."
\end{mdframed}
\todo{@assign: Tomek}

\begin{mdframed}[style=comment] 
Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution.

- There is a superfluous word (dealing/working). I think this would read better as "Nevertheless, when working with only a part of the sphere, the border slightly affects the convolution."
\end{mdframed}
We have corrected this mistake according to the reviewer suggestion.

@@

\begin{mdframed}[style=comment] 
These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.

- Are they really mitigated? Surely there are still effects but you are happy with the level?
\end{mdframed}
\todo{Assign: @nati, @michael}

\begin{mdframed}[style=comment] 
Furthermore, this result is another sign that the constructed graph is able to capture the spherical structure of the HEALPix sampling.

- What does "this" refer to?
\end{mdframed}
We have clarifed the sentence as:
\begin{mdframed}[style=manuscript] 
Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical
structure of the HEALPix sampling. 
\end{mdframed}

@@

\begin{mdframed}[style=comment] 
In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.

- I think it might be another one of the most important points in the paper which allows you to justify why not being exact (like a spherical harmonic transform) is acceptable. If I were you I'd move this into the main body of the paper.
\end{mdframed}
\todo{Assign: @all, \nati{What do you think? I had the feeling we already have that in the main body of the paper. I cannot remember where, though.}}

\begin{mdframed}[style=comment] 
We then plot the result with a gnomonic projection.

- Can you add in Figure C.16 here. "We then plot the result with a gnomonic projection, as shown in Figure C.16". Also, why do you choose a gnomonic projection? In fact, with plots C.16 and C.17 I would make them a single plot (as in Figure. 10),
\end{mdframed}
Inspired by the reviewer comment, we have merged the three plots in a single figure and adapted the text accordingly.

### 2019-01-27 scnn.tex
after a small second pass

\nati{Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the Manifold and a fully connected graph built with exponentially decaying weights.
While our construction will not exactly respect the setting defined by \citep{belkin2007convergence} (the sampling is not uniform and the graph is not fully connected), we observe empirically strong evidence of convergence.}

@@

Thanks to their versatility, graph neural networks have been used in a variety of tasks, such as identifying diseases from brain connectivity networks \citep{ktena2018metriclearning} or population graphs \citep{parisot2017disease}, designing drugs using molecular graphs \citep{hop2018drugdesign}, segmenting 3D point clouds \citep{qi2017pointcloudsegmentation}, optimizing shapes to be aerodynamic \citep{baque2018shape}, and many more.
By interwinding graph convolutional layers and recurrent layers \citep{seo2016gcrn}, they can for example model structured time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
Another trend, parallel to the modelling of structured data, is the use of graph neural networks for relational reasoning \citep{battaglia2018review}.

@@

Spherical CNNs are so far mostly used for omnidirectional imaging.
Many scientific fields, such as weather or climate modelling, would however benefit from an efficient and versatile spherical CNN.
With this work, we hope to demonstrate and help democratize the use of those tools for spherical data analysis.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{subspace_harmonics_eigenvectors}
	\caption{Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics. Each pixel on the plot is the dot product between one spherical harmonic and one graph Fourier mode $\b u_i$. The plot clearly shows how the subspaces are aligned: modes and harmonics that correspond to different degrees $\ell$ are mostly orthogonal to each other, while modes and harmonics that correspond to the same degree $\ell$ are linearly dependent. There are $2 \ell + 1$ orders per degree $\ell$. Moreover, we see that the Fourier modes have the correct symmetries, indicated by the perfect orthogonality between even and odd functions. For example, the modes corresponding to $\ell=7$ are perfectly orthogonal to the harmonics corresponding to $\ell=0,2,4,6,8$.}
	\label{fig:subspace_harmonics_eigenvectors}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=\linewidth]{gaussian_filters_sphere}
  \caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
  Top: Diffusion of a unit of heat for different times $t$ using the graph.
  Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
  Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
}
  \label{fig:gaussian_filters_comparizon}
\end{figure}

Furthermore, the harmonics ressemblance is another sign that the constructed graph is able to capture the spherical
structure of the HEALPix sampling. In some applications, where the
exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.

>>>>

\nati{Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
While our construction will not exactly respect the setting defined by \citep{belkin2007convergence} (the sampling is not uniform and the graph is not fully connected), we observe empirically strong evidence of convergence.}

@@

Thanks to their versatility, graph neural networks have been used in a variety of tasks, such as identifying diseases from brain connectivity networks \citep{ktena2018metriclearning} or population graphs \citep{parisot2017disease}, designing drugs using molecular graphs \citep{hop2018drugdesign}, segmenting 3D point clouds \citep{qi2017pointcloudsegmentation}, optimizing shapes to be aerodynamic \citep{baque2018shape}, and many more.
By interwinding graph convolutional layers and recurrent layers \citep{seo2016gcrn}, they can for example model structured time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
Another trend, parallel to the modeling of structured data, is the use of graph neural networks for relational reasoning \citep{battaglia2018review}.

@@

Spherical CNNs are so far mostly used for omnidirectional imaging.
Many scientific fields, such as weather or climate modeling, would however benefit from an efficient and versatile spherical CNN.
With this work, we hope to demonstrate and help democratize the use of those tools for spherical data analysis.

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=\linewidth]{subspace_harmonics_eigenvectors}
	\includegraphics[width=\linewidth]{figures/subspace_alignment_percentage.pdf}
	\caption{Top: Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics. Each pixel on the plot is the dot product between one spherical harmonic and one graph Fourier mode $\b u_i$. The plot clearly shows how the subspaces are aligned: modes and harmonics that correspond to different degrees $\ell$ are mostly orthogonal to each other, while modes and harmonics that correspond to the same degree $\ell$ are linearly dependent. There are $2 \ell + 1$ orders per degree $\ell$. Moreover, we see that the Fourier modes have the correct symmetries, indicated by the perfect orthogonality between even and odd functions. For example, the modes corresponding to $\ell=7$ are perfectly orthogonal to the harmonics corresponding to $\ell=0,2,4,6,8$.
	\nati{Bottom: Evolution of the allignement of the graph Fourier mode and the spherical harmonics for with respect of the speherical harmonic index $\ell$. It is the percentage of energy contained in the diagonal blocks of the correlation matrix plotted on top.}}
	\label{fig:subspace_harmonics_eigenvectors}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=\linewidth]{gaussian_filters_sphere}
  \caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
  Top: Diffusion of a unit of heat for different times $t$ using the graph.
  Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
  Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
}
  \label{fig:gaussian_filters_comparizon}
\end{figure}
Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical
structure of the HEALPix sampling. In some applications, where the
exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.
